%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------
\documentclass[a4paper,11pt]{article}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	
\usepackage{amsmath} 	
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[top=0.35in, bottom=0.35in, left=0.5in, right=0.5in]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{supertabular}
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}
\usepackage[unicode, draft=false]{hyperref}
\usepackage{fontawesome5}

\usepackage[T1]{fontenc}
\usepackage{inter} % Modern, clean sans-serif font
\renewcommand{\familydefault}{\sfdefault}

% Layout settings
\newcolumntype{C}{>{\centering\arraybackslash}X} 

% Color Definitions
\definecolor{primaryColor}{RGB}{0, 79, 158} % Professional Deep Blue
\definecolor{textColor}{RGB}{40, 40, 40}
\definecolor{subtleGray}{RGB}{120, 120, 120}

% CRITICAL: Section style for modern look
\titleformat{\section}{\large\bfseries\color{primaryColor}\scshape\raggedright}{}{0em}{}[\color{primaryColor}\titlerule]

% Spacing between sections
\titlespacing{\section}{0pt}{8pt}{4pt}

\hypersetup{colorlinks,breaklinks,urlcolor=primaryColor,linkcolor=primaryColor}

\begin{document}
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE / HEADER
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\color{primaryColor}\Huge\textbf{UDAY SINGH BOHRA} \\[2pt]
\large\textcolor{subtleGray}{Full Stack Developer $|$ MERN Stack Specialist} \\[4pt]
\small
\href{https://github.com/UdayBohra7}{\raisebox{-0.05\height}\faGithub\ GitHub} \ $|$ \  
\href{https://www.linkedin.com/in/udaybohra7/}{\raisebox{-0.05\height}\faLinkedin\ LinkedIn} \ $|$ \  
\href{mailto:bohrauday09@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ bohrauday09@gmail.com} \ $|$ \  
\href{tel:+916397515520}{\raisebox{-0.05\height}\faMobile \ 6397515520} \\
\textcolor{subtleGray}{Mohali, Punjab, India} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------
\section{Professional Summary}
Innovative \textbf{Full Stack Developer} with 2+ years of experience in the \textbf{MERN stack} and AI integration. Expert in architecting scalable web applications, secure payment systems, and AI-driven diagnostic tools that optimize operational efficiency.

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\linewidth}{@{}l >{\raggedright\arraybackslash}X@{}}
\textbf{Frontend:} & JavaScript, React.js, Next.js, TypeScript, Shopify-Remix, Tailwind CSS. \\
\textbf{Backend:} & Node.js, Express.js, MongoDB, Mongoose, RESTful APIs. \\
\textbf{Payments:} & Stripe, PayPal, In-App Purchase (IAP) Backend APIs. \\
\textbf{Tools/Cloud:} & AWS S3 Buckets, Firebase, Supabase, Zod, Joi, Swagger, JWT, PrintNode API. \\
\textbf{AI Integration:} & OpenAI, Gemini, Perplexity, Auto Content API, AI Code Auditing. \\
\end{tabularx}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{MERN Stack Developer} & \hfill March 2025 -- April 2026 \\[1.2pt]
\textbf{Esferasoft Pvt. Ltd., Mohali, Punjab} & \hfill \\
\multicolumn{2}{@{}X@{}}{
Architected \textbf{secure payment infrastructures} and \textbf{AI-driven workflows} using LLM APIs, streamlining 40\% of content generation. Optimized \textbf{cloud resource management} and schema validation, reducing media upload latency by 30\% while ensuring 100\% data integrity.
}
\end{tabularx}

\vspace{4pt} 

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{MERN Stack Developer} & \hfill Feb 2024 -- Feb 2025 \\[1.2pt]
\textbf{Beatum IT Solutions Pvt. Ltd., Mohali, Punjab} & \hfill \\
\multicolumn{2}{@{}X@{}}{
Engineered \textbf{subscription systems} and digital asset APIs for 5,000+ monthly users. Designed modular \textbf{component libraries} improving dev speed by 20\%, and enhanced \textbf{RESTful API architectures} to boost server-side response times by 25\%.
}
\end{tabularx}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\textbf{Marissa Meals (Full Stack MERN)} \\
Full-stack health app featuring \textbf{affiliate products} and AI media processing. Leveraged multimodal AI for tracking 200+ food items with secure \textbf{JWT authentication}.

\vspace{2pt}
\textbf{Vellay AI (AI Skin \& Hair Analysis)} \\
Built an AI-driven platform for \textbf{skin and hair diagnostics} using multimodal models. Developed scalable APIs for \textbf{personalized care routines}, weather-based recommendations, and scan history tracking.

\vspace{2pt}
\textbf{Wardrobe (E-commerce API Architecture)} \\
Architected a scalable RESTful API with \textbf{In-App Purchase support} and Role-Based Access Control (RBAC). Documented with Swagger to reduce frontend-backend integration time by 30\%.

\vspace{2pt}
\textbf{Order-Print (Next.js \& PrintNode Integration)} \\
Streamlined a specialized order management platform integrated with \textbf{Shopify}. Engineered programmatic remote printing using \textbf{PrintNode} and Firebase for real-time tracking. Audited and remediated AI-generated code from FireStudio to resolve complex logic bugs, reducing sync latency by 35\%.

\vspace{2pt}
\textbf{My Podcast Today (AI Voice Synthesis)} \hfill \href{https://mypodcasttoday.com/login}{Link} \\
AI-powered platform for podcast generation, integrating \textbf{Auto Content API} and Google Text-to-Speech to automate 90\% of the audio production workflow for end-users.

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2020 -- 2023 & B.Tech in CSE -- \textbf{Uttarakhand Technical University} \\ 
2017 -- 2020 & Diploma in CSE -- \textbf{Govt. Polytechnic College Kotabagh, Nainital} \\ 
\end{tabularx}

\end{document}